Mahotas: Open source software for scriptable computer vision

### 2012-08-29 paper.tex
BIB Add affiliations to contributors

\textbf{List of contributors}\\
Luis Pedro Coelho, Zachary Pincus, Peter J. Verveer, Davis King, Robert Webb
(Carnegie Mellon University), Matthew Goodman, K.-Michael Aye (University of
Bern), Rita Simões, Joe Kington (University of Wisconsin Dept. of Geoscience),
Christoph Gohlke (University of California, Irvine), and Sandro Knauss.

>>>>

\textbf{List of contributors}\\
Luis Pedro Coelho (Carnegie Mellon University and Instituto de Medicina
Molecular), Zachary Pincus (Stanford University), Peter J. Verveer (European
Molecular Biology Laboratory), Davis King (Northrop Grumman ES), Robert Webb
(Carnegie Mellon University), Matthew Goodman (University of Texas at Austin),
K.-Michael Aye (University of Bern), Rita Sim\~{o}es (University of Twente),
Joe Kington (University of Wisconsin Dept.  of Geoscience), Christoph Gohlke
(University of California, Irvine), and Sandro Knauss (University of Bremen).
